Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-24 main.tex
backing up figures that have already been finished

\usepackage{xifthen}
\usepackage[utf8]{inputenc}
\usepackage{dashbox}
\usepackage{ebproof}
\usepackage{amsmath}
\usepackage{ebproof}
%\usepackage{stmaryrd}
\usepackage{virginialake}
\vlstemheight=12pt

@@

\usepackage{tikz}
\usepackage{amsthm}\theoremstyle{plain}
\newtheorem{thm}{Theorem}%[section]
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{proposition}[thm]{Proposition}
\newtheorem{theorem_}[thm]{Theorem}

@@

>>>>

\usepackage{xifthen}
\usepackage[utf8]{inputenc}
\usepackage{dashbox}
\usepackage{ebproof}
%\usepackage{mathtools}% mathtools = bug-fixed amsmath; includes variable length \mapsto as \xmapsto
\usepackage{amsmath}
\usepackage{ebproof}
%\usepackage{stmaryrd}
\usepackage{virginialake}
\vlstemheight=12pt

@@

%%%%%%%%% PACKAGES DOMINIC USES FOR CP FIGURES
\usepackage{tikz}
\usetikzlibrary{arrows}% e.g. >=latex' or >=stealth'
\usetikzlibrary{decorations}\usetikzlibrary{shapes.geometric}% better dot/dash in cp fibres
\usetikzlibrary{chains}% for inline skew fibrations on formulas
\usepackage{calculator}% e.g. \MULTIPLY{1.3}{4.2}{\resultmacroname} https://tug.org/TUGboat/tb33-3/tb105fuster.pdf  https://mirror.hmc.edu/ctan/macros/latex/contrib/calculator/calculator.pdf

\usepackage{amsthm}\theoremstyle{plain}
\newtheorem{thm}{Theorem}%[section]
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{proposition}[thm]{Proposition}
\newtheorem{theorem_}[thm]{Theorem}

@@

\subsection{Pictures}

\input{pics.tex}
The fograph of drinker formula $\drinkerformula=\veedrinkerformula$:
%
\begin{center}\vspace{2ex}\begin{tikzpicture}
\drinkerbase
\end{tikzpicture}\vspace{1ex}\end{center}
%
A combinatorial proof of drinker formula $\drinkerformula=\veedrinkerformula$:
%
\begin{center}\vspace{2ex}\begin{tikzpicture}
\drinkerfibcoloured
\end{tikzpicture}\vspace{1ex}\end{center}
%
Condensed combinatorial proof of drinker formula(s):
%
\begin{center}\vspace{3ex}\begin{math}
\begin{tikzpicture}
\drinkerInline
\end{tikzpicture}
\hspace{10ex}
\begin{tikzpicture}
\veedrinkerInline
\end{tikzpicture}\end{math}\end{center}

\figcps Fig.\,\ref{fig:cps} is a floating figure with four combinatorial proofs.

\figcpscondensed Fig.\,\ref{fig:cps-condensed} is a floating figure with the condensed forms of the four combinatorial proofs in Fig.\,\ref{fig:cps}.

Both $\veedrinkerformula$ and $\variantveedrinkerformula$ have the same
rectified fograph $\drinkergraph$, shown below-left.
%
\begin{center}\begin{math}
%
\drinkergraphpic
%
\hspace{8ex}
%
\drinkercotreepic
%
\hspace{8ex}
%
\drinkerbindinggraphpic
%
\end{math}\end{center}

Lifting diagrams:
%
\liftingdiagrams

\figdrinkerbifib Fig.\,\ref{fig:drinkerbifib} shows the drinker bifibration, binding fibration, and skeleton.
